DeepPicar: A Low-cost Deep Neural Network-based Autonomous Car

### 2018-04-20 paper/evaluation-drampart.tex
..

In this subsection, we examine the CNN workload's memory bandwidth
sensitivity and the effect of memory bandwidth throttling in providing
isolation. For the experiments, we use MemGuard\cite{Yun2013}, which 
can limit the amount of memory bandwidth each core receives. MemGuard
operates periodically, at a 1 ms interval, and uses hardware
performance counters to throttle cores if they exceed their given
bandwidth budgets within each regulation period (i.e., 1 ms) by
scheduling high-priority idle kernel threads, until the next period begins.

@@

Figures \ref{fig:memguard_bandwidth} shows the results.
Note that, in case of BwWrite co-runners, we have assigned half the
bandwidth budget because MemGuard currently only accounts for L2 refills
but not write-backs, which effectively allows twice the allocated
memory bandwidth budget. Regardless, the results clearly show that
limiting the co-runners's memory bandwidth is effective in protecting the
CNN model's performance.

>>>>

In this subsection, we examine the CNN workload's memory bandwidth
sensitivity and the effect of memory bandwidth throttling in providing
isolation. For the experiments, we use MemGuard\cite{Yun2013}, a Linux
kernel module that can limit the amount of memory bandwidth each core
receives. MemGuard
operates periodically, at a 1 ms interval, and uses hardware
performance counters to throttle cores, if they exceed their given
bandwidth budgets within each regulation period (i.e., 1 ms), by
scheduling high-priority idle kernel threads until the next period begins.

@@

Figures \ref{fig:memguard_bandwidth} shows the results.
As clearly can be seen in the figure, limiting the co-runners's memory
bandwidth is effective in protecting the CNN model's performance for
BwRead and BwWrite co-runners. The benefits are especially more
pronounced in case of BwWrite co-runners as we throttle them more the
CNN's performance quickly improves.

%% Note that, in case of BwWrite co-runners, we assign half the
%% bandwidth budget because MemGuard only accounts for L2 refills
%% but not write-backs, which effectively allows twice the allocated
%% memory bandwidth budget.
